Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-04-02 parts/def-ph.tex
update notations
section 3

\begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
\label{def:ph}
  If $k \in \sN^*$, a \emph{Process Hitting with $k$ priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, and:
  \begin{itemize}
    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$. Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_l} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_l) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_l \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
  \end{itemize}
  We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
\end{definition}

@@

\pref{def:chainsactions} defines chains of uncontrollable actions,
and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains to avoid incoherent states between cooperative sorts.
\begin{definition}
\label{def:chainsactions}
  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
  \begin{align*}
  \PHh(a, b) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = a \wedge \PHsort(\PHtarget(h_s)) = b \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
  \end{align*}
\end{definition}
\begin{criterion}[Cycle-freeness between actions of priority $1$]
\label{cr:cyclefreeness}
%\paragraph{Cycle-freeness between actions of priority $1$}
  There is no cycle in chains of actions:
  $$\forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.$$
\end{criterion}

>>>>

\begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
\label{def:ph}
  If $k \in \sN^*$, a \emph{Process Hitting with $k$ priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, and:
  \begin{itemize}
    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
    %$\PHl \DEF \prod_{a \in \PHs} \PHl_a$
    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$. Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_l} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_l) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_l \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
  \end{itemize}
  We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
\end{definition}

@@

\pref{def:chainsactions} defines chains of uncontrollable actions,
and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains to avoid incoherent states between cooperative sorts.
\begin{definition}
\label{def:chainsactions}
  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
  \begin{align*}
  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
  \end{align*}
\end{definition}
\begin{criterion}[Cycle-freeness between actions of priority $1$]
\label{cr:cyclefreeness}
%\paragraph{Cycle-freeness between actions of priority $1$}
  There is no cycle in chains of actions:
  $$\forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.$$
\end{criterion}
